### 2014-03-12 src/methodology.Rnw
update

We used several different sampling criterias, based on different strategies of sampling, and what happens when the number of mutants selected falls below a threshold.

>>>>

We used several different sampling criteria. We varied the criterias based on the granularity and
scope of sampling, and strategy chosen when the number of mutants to be sampled falls below one.
